Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-19 bdcloud_paper/latex/paper.tex
Added references to introduction

\emph{Ab initio} mathematical models for generating synthetic data overcomes several of these obstacles.  The code for generating the data is often small, enabling free hosting, licensing restrictions are often avoided, and the data size can be scaled, enabling seamless usage of the same data set across a range of scenarios.  Common synthetic data set generators such as TeraGen and the Intel Hadoop Benchmark \textcolor{red}{reference} can generate data sets quickly and at any scale, but they are over-specialized for benchmarking, resulting in semantically-void data that lacks usefulness for analytics examples. The lack of frameworks for generating semantically-rich data at arbitrary scale denies developers access to consistent data sets that can be used across a range of environments \textcolor{red}{Huppler, Pavlo}.  \textcolor{red}{standard benchmarks}

Attempts have been made to find a middle-ground.  Myriad and PDGF provide primitives for specifying generative data models \textcolor{red}{reference}. Alexandrov, et al. proposed Oligos, an approach for generating synthetic data from models trained on reference databases with real data \textcolor{red}{reference}. Oligos appears promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models.  Until such methods have reached maturity, development of a customized domain-driven model is best suited for generating for satisfying the needs of big data software and algorithms development.

The BigPetStore application aims to be a big data application blueprint built around a fictional chain of pet stores, which incorporates a data generator and complex examples of cleaning, aggregation, and analytics using well-known tools such as Hive and Mahout from across the Hadoop and Spark ecosystems \textcolor{red}{reference}. BigPetStore's usefulness has been demonstrated by its incorporation into the Apache BigTop distribution \cite{BigTop} for testing and as a reference application.

In this work, we present a new domain-drive model and simulation for generating arbitrarily large, complex data for testing and benchmarking of software tools in the big data space. Compared with BigPetStore's previous data generator, our model and implementation can generate data which contains geospatial, temporal, and quantitative features, similar to the type of data which businesses and organizations might typically encounter. Combining the features of the TeraGen (scalability) \textcolor{red}{reference} and MovieLens (semantically rich) \textcolor{red}{reference} input data sets commonly used for big data benchmarking, we present a scalable synthetic data set generation implementation which can be used to benchmark lower level tasks (such as sorting) as well as higher level tasks (such as clustering, recommending, and search indexing) at arbitrary scale.  To validate this approach, we apply it as a drop in replacement for the current version of BigPetStore which has already been utilized to test several Hadoop deployments at terabyte scale, and is actively being adopted by a variety of companies in the software industry, and confirm that it generates data with desirable properties (global patterns and region specific transactions).

>>>>

Methods for generating synthetic data offer multiple advantages over pre-generated data sets.  The code for generating the data is often small, making it easy and cheap to host, transfer, and store. Licensing restrictions and data privacy issues are avoided \textcolor{red}{cite}.  And, the size of the data sets can be scaled arbitrarily, enabling seamless usage of the same data set across a range of situations.

Multiple synethic data set generators exist.  TeraGen \textcolor{red}{cite} and the Intel Hadoop Benchmark Suite \cite{Huang2010} can generate data sets quickly and at any scale. Targetted towards specific benchmarks such as Map-Reduce jobs and Hive queries, the resulting data is semantically-void and not useful for other tasks.  The PGDF (Parallel Data Generation Framework) can quickly generate data and queries that structurally satifies a user-defined relational database schema \cite{Ghazal2013,Rabl2011a,Frank2012,Rabl2011}. The Myriad Toolkit improves on PGDF through a more descriptive model specification language \cite{Alexandrov2012}. Myriad allows the user to specify the distributions for sampling values, simple arithmetic equations for setting the value of fields from other fields, and restrictions on fields domains. Due to the inability to specify underlying dynamic models with latent variables, the data generated by PGDF and Myriad lacks informational complexity and genuine semantics, making it inapprioriate for analytics.

More advanced approaches such as Oligas \cite{Alexandrov2013} and SMOTE \cite{Chawla2002} attempt to generate or extend real data sets with synthetic data sets that satisfy characteristics learned from a real reference data sets. \textcolor{red}{privacy, accuracy without details of underlying process, SMOTE - feature space} Oligos appears promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models.

Until such methods have reached maturity, the development of customized, domain-driven models is best suited for generating for satisfying the needs of big data software and algorithms development. For example, the Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006} was developed for the Department of Homeland Security to develop synthetic data for effectiveness of IDASs designed to identify potential terrorism threat scenarios.

. The lack of frameworks for generating semantically-rich data at arbitrary scale denies developers access to consistent data sets that can be used across a range of environments \textcolor{red}{Huppler, Pavlo}.  \textcolor{red}{standard benchmarks}

The BigPetStore application aims to be a big data application blueprint built around a fictional chain of pet stores, which incorporates a data generator and complex examples of cleaning, aggregation, and analytics using well-known tools such as Hive and Mahout from across the Hadoop and Spark ecosystems \textcolor{red}{reference}. BigPetStore's usefulness has been demonstrated by its incorporation into the open-source Apache BigTop distribution \cite{BigTop} for testing and as a reference application.

In this work, we present a new domain-driven model and simulation for generating arbitrarily large, complex data for testing and benchmarking of algorithms, software, and infrastructure in the big data space. Compared with BigPetStore's previous data generator, our model and implementation can generate data which contains geospatial, temporal, and quantitative features, similar to the type of data which businesses and organizations might typically encounter. Combining the features of the TeraGen (scalability) \textcolor{red}{reference} and MovieLens (semantically rich) \textcolor{red}{reference} input data sets commonly used for big data benchmarking, we present a scalable synthetic data set generation implementation which can be used to benchmark lower level tasks (such as sorting) as well as higher level tasks (such as clustering, recommending, and search indexing) at arbitrary scale.  To validate this approach, we apply it as a drop in replacement for the current version of BigPetStore which has already been utilized to test several Hadoop deployments at terabyte scale, and is actively being adopted by a variety of companies in the software industry, and confirm that it generates data with desirable properties (global patterns and region specific transactions).
